The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-12 draft/ms.tex
Section 5 update and comments from Jason are included

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future}\label{sec:conclusion}

Any planned future improvements and updates?

>>>>

ZZZ (1) We have a list of criteria for 'robustly detected' imaging planets (on our methodology web page) - do we have similar lists of criteria regarding 'robust detections' for microlensing, timing, and astrometry planets?

No, not really.  As I think we discuss in the last EOD paper (check) we relax some conditions for transiting planets (we don't have to have a measured RV amplitude, for instance).  There have been no astrometric planets.  Timing planets must have dynamically stable orbits and, ideally, show multiple complete orbits (see Jackson Norris's paper for a discussion of difficulties with timing planets, also cite recent papers by Rob Wittenmyer).  In general, we accept microlensing planets that are appear in refereed journals as having unambiguously planetary masses.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Future Work}\label{sec:conclusion}

We have had two major updates since \cite{Wright2011}. We included Kepler planet candidates and other planets on exoplanets.org. Although they are not included in the EOD, we reported them on our website to help the users explore them and use them easily. We also have added some new fields, removed obsolete fields and revised them as necessary.

ZZZ Any planned future improvements and updates?
I hesitate to promise here, lest we overpromise.  We do hope to include images of directly imaged planets (where allowed under copyright law) and perhaps light curves for transits.
